\section{References}

Cloud Migration
  - (Oracle) \url{https://www.infosys.com/Oracle/white-papers/Documents/cloud-migration-assessment-framework.pdf}


 \noindent [1] Sommerville, I. (2020). Engineering Software Products: An Introduction to Modern Software Engineering. Global edition. USA:Pearson.
 \vspace{0.2cm}

 \noindent [2] StackOverflow. (2023) \textit{Stack Overflow Developer Survey 2023} [online]. Available at \url{https://survey.stackoverflow.co/2023/#cloud-platforms} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [3] Amazon Web Services. (2023) \textit{What is Cloud Native? - Everything you need to know - AWS} [online]. Available at \url{https://aws.amazon.com/what-is/cloud-native/} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [4] IBM. (2023) \textit{What is Virtualization? | IBM} [online]. Available at \url{https://www.ibm.com/topics/virtualization} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [5] Firesmith, D. (2017) \textit{Virtualization via Virtual Machines} [online]. Available at \url{https://insights.sei.cmu.edu/blog/virtualization-via-virtual-machines/} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [6] Amazon Web Services. (2023) \textit{Free Cloud Computing Services - AWS Free Tier} [online]. Available at \url{https://aws.amazon.com/free/} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [7] IBM. (2023) \textit{What are microservices? | IBM} [online]. Available at \url{https://www.ibm.com/topics/microservices} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [8] Amazon Web Services. (2023) \textit{Global Infrastructure Regions \& AZs} [online]. Available at \url{https://aws.amazon.com/about-aws/global-infrastructure/regions_az/} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [9] Alphabet Inc. (2023) \textit{Shared responsibilities and shared fate on Google Cloud | Architecture Framework} [online]. Available at \url{https://cloud.google.com/architecture/framework/security/shared-responsibility-shared-fate} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [10] Amazon Web Services. (2023) \textit{Shared Responsibility Model - Amazon Web Services (AWS)} [online]. Available at \url{https://aws.amazon.com/compliance/shared-responsibility-model/} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [11] Microsoft. (2023) \textit{Shared responsibility in the cloud - Microsoft Azure | Microsoft Learn} [online]. Available at \url{https://learn.microsoft.com/en-us/azure/security/fundamentals/shared-responsibility} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [12] Ozkaya, M. (2021) \textit{Scalability — Vertical or Horizontal Scaling when Designing Architectures} [online]. Available at \url{https://medium.com/design-microservices-architecture-with-patterns/scalability-vertical-scaling-horizontal-scaling-adb52ff679f} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [13] WebAiry. (2019) \textit{Horizontal and Vertical Scaling} [online]. Available at \url{https://www.webairy.com/horizontal-and-vertical-scaling/} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [14] Tidy, J. (2023) \textit{MOVEit hack: BBC, BA and Boots among cyber attack victims} [online]. Available at \url{https://www.bbc.co.uk/news/technology-65814104} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [15] IBM. (2023) \textit{What is Infrastructure as Code (IaC)?} [online]. Available at \url{https://www.ibm.com/topics/infrastructure-as-code} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [16] Amazon Web Services. (2023) \textit{Announcing the end of support for Node.js 12.x in the AWS SDK for JavaScript (v3)} [online]. Available at \url{https://aws.amazon.com/blogs/developer/announcing-the-end-of-support-for-node-js-12-x-in-the-aws-sdk-for-javascript-v3/} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [17] Peterson, B. (2023) \textit{PEP 387 - Backwards Compatibility Policy} [online]. Available at \url{https://peps.python.org/pep-0387/} (accessed 11th August).
 \vspace{0.2cm}

 \noindent [18] Villamizar, M., Oscar Garcés, et al. (2017) \textit{Cost comparison of running web applications in the cloud using monolithic, microservice, and AWS Lambda architectures} [online]. Available at \url{https://link.springer.com/article/10.1007/s11761-017-0208-y#Sec15} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [19] Kolny, M. (2023) \textit{Scaling up the Prime Video audio/video monitoring service and reducing costs by 90\%} [online]. Available at \url{https://www.primevideotech.com/video-streaming/scaling-up-the-prime-video-audio-video-monitoring-service-and-reducing-costs-by-90} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [20] Solanki, R. (2019) \textit{Why a slow website is killing your conversions} [online]. Available at \url{https://www.thedrum.com/opinion/2019/08/28/why-slow-website-killing-your-conversions} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [21] Website Optimization. (2008) \textit{The Psychology of Web Performance - how slow response times affect user psychology} [online]. Available at \url{https://www.websiteoptimization.com/speed/tweak/psychology-web-performance/} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [22] Charles, J. (2018) \textit{What is Debouncing?} [online]. Available at \url{https://medium.com/@jamischarles/what-is-debouncing-2505c0648ff1} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [23] Baldwin, A. (2021) \textit{Peer-to-Peer in Blockchain: how it works} [online]. Available at \url{https://www.cryptopolitan.com/peer-to-peer-in-blockchain-how-it-works/} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [24] IBM. (2023) \textit{What are smart contracts on blockchain?} [online]. Available at \url{https://www.ibm.com/topics/smart-contracts} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [25] Solidity Team. (2023) \textit{Home | Solidity Programming Language} [online]. Available at \url{https://soliditylang.org/} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [26] Alici, I, U. et al. (2023) \textit{OpenAI ChatGPT for Smart Contract Security Testing: Discussion and Future Directions} [online]. Available at \url{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4412215} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [27] QuillAudits Team. (2023) \textit{Beyond the Hype: ChatGPT and Smart Contract Auditing QuillAudits Team} [online]. Available at \url{https://blog.quillaudits.com/2023/04/03/beyond-the-hype-chatgpt-and-smart-contract-auditing/} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [28] Sommerville, I. (2016). Software Engineering. Tenth edition. USA:Pearson.
 \vspace{0.2cm}
 
 \noindent [29] Raza, M. (2020) \textit{Reliability vs Availability: What's The Difference?} [online]. Available at \url{https://www.bmc.com/blogs/reliability-vs-availability/} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [30] Caballar, D, R. (2023) \textit{The Move to Memory-Safe Programming} [online]. Available at \url{https://spectrum.ieee.org/memory-safe-programming-languages} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [31] Prechelt, L. (2000) \textit{An Empirical Comparison of Seven Programming Languages} [online]. Available at \url{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.113.1831&rep=rep1&type=pdf} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [32] CyberArk. (2023) \textit{What is Least Privilege? Principle of Least Privilege Definition} [online]. Available at \url{https://www.cyberark.com/what-is/least-privilege/} (accessed 15th August).
 \vspace{0.2cm}

 \noindent [33] OWASP. (2021) \textit{OWASP Top Ten} [online]. Available at \url{https://owasp.org/www-project-top-ten/} (accessed 15th August).
 \vspace{0.2cm}

 \noindent [34] Sommerville, I. (2019) \textit{Error prone constructs} [online]. Available at \url{https://software-engineering-book.com/web/error-prone-constructs/} (accessed 15th August).
 \vspace{0.2cm}

 \noindent [35] Munoz, D. (2021) \textit{What is DRY Code} [online]. Available at \url{https://codinglead.co/javascript/what-is-DRY-code} (accessed 15th August).
 \vspace{0.2cm}

 \noindent [36] Fulber-Garcia, V. (2023) \textit{Antipatterns: Magic Numbers} [online]. Available at \url{https://www.baeldung.com/cs/antipatterns-magic-numbers} (accessed 15th August).
 \vspace{0.2cm}

 \noindent [37] Amazon Web Services. (2023) \textit{Alarm events and EventBridge} [online]. Available at \url{https://docs.aws.amazon.com/AmazonCloudWatch/latest/monitoring/cloudwatch-and-eventbridge.html} (accessed 15th August).
 \vspace{0.2cm}

 \noindent [38] Jenkins. (2023) \textit{Jenkins} [online]. Available at \url{https://www.jenkins.io/} (accessed 15th August).
 \vspace{0.2cm}

 \noindent [39] Roy, D. (2023) \textit{Safety and Security Engineering} [online]. Available at \url{https://vle.aston.ac.uk/bbcswebdav/pid-3316291-dt-content-rid-24421304_1/xid-24421304_1} (accessed 15th August).
 \vspace{0.2cm}

 \noindent [40] Tidy, J. (2020) \textit{Police launch homicide inquiry after German hospital hack} [online]. Available at \url{https://www.bbc.co.uk/news/technology-54204356} (accessed 15th August).
 \vspace{0.2cm}

 \noindent [41] UK Government. (2023) \textit{Check someone's driving licence information} [online]. Available at \url{https://www.gov.uk/check-driving-information} (accessed 16th August).
 \vspace{0.2cm}

 \noindent [42] McAfee LLC. (2023) \textit{What Are Tailgating Attacks and How to Protect Yourself From Them} [online]. Available at \url{https://www.mcafee.com/blogs/internet-security/what-are-tailgating-attacks/} (accessed 16th August).
 \vspace{0.2cm}

 \noindent [43] Winder, D. (2022) \textit{LastPass Hacked: Password Manager With 25 Million Users Confirms Breach} [online]. Available at \url{https://www.forbes.com/sites/daveywinder/2022/08/25/lastpass-hacked-password-manager-with-25-million-users-confirms-breach/} (accessed 16th August).
 \vspace{0.2cm}

 \noindent [44] Hunt, T. (2023) \textit{Have I Been Pwned: Check if your email has been compromised in a data breach} [online]. Available at \url{https://haveibeenpwned.com/} (accessed 16th August).
 \vspace{0.2cm}

 \noindent [45] Cisco Systems Inc. (2023) \textit{What Is Penetration Testing?} [online]. Available at \url{https://www.cisco.com/c/en/us/products/security/what-is-pen-testing.html#~types-of-pen-testing} (accessed 22nd August).
 \vspace{0.2cm}

 \noindent [46] Poston, H. (2020) \textit{What are black box, grey box, and white box penetration testing?} [online]. Available at \url{https://resources.infosecinstitute.com/topics/penetration-testing/what-are-black-box-grey-box-and-white-box-penetration-testing/} (accessed 22nd August).
 \vspace{0.2cm}

 \noindent [47] Evalian. (2023) \textit{Penetration testing costs: A comprehensive guide} [online]. Available at \url{https://evalian.co.uk/a-comprehensive-guide-to-understanding-penetration-testing-costs/} (accessed 22nd August).
 \vspace{0.2cm}

 \noindent [48] Chekalov, M. (2023) \textit{22 Insider Threat Statistics to Look Out For in 2023} [online]. Available at \url{https://techjury.net/blog/insider-threat-statistics/} (accessed 22nd August).
 \vspace{0.2cm}

 \noindent [49] GitLab B.V. (2023) \textit{What is a code review?} [online]. Available at \url{https://about.gitlab.com/topics/version-control/what-is-code-review/} (accessed 23rd August).
 \vspace{0.2cm}

 \noindent [50] Lakshmanan, R. (2023) \textit{11 Malicious PyPI Python Libraries Caught Stealing Discord Tokens and Installing Shells} [online]. Available at \url{https://thehackernews.com/2021/11/11-malicious-pypi-python-libraries.html} (accessed 23rd August).
 \vspace{0.2cm}

 \noindent [51] AO Kaspersky Lab. (2023) \textit{What is Typosquatting?} [online]. Available at \url{https://www.kaspersky.com/resource-center/definitions/what-is-typosquatting} (accessed 23rd August).
 \vspace{0.2cm}

 \noindent [52] Amazon Web Services. (2023) \textit{Web Application Firewall, Web API Protection - AWS WAF - AWS} [online]. Available at \url{https://aws.amazon.com/waf/} (accessed 23rd August).
 \vspace{0.2cm}

 \noindent [53] Cloudflare Inc. (2023) \textit{What is a distributed denial-of-service (DDoS) attack? | Cloudflare} [online]. Available at \url{https://www.cloudflare.com/en-gb/learning/ddos/what-is-a-ddos-attack/} (accessed 23rd August).
 \vspace{0.2cm}

 \noindent [54] Roy, D. (2023) \textit{Deployment and Software Evolution} [online]. Available at \url{https://vle.aston.ac.uk/bbcswebdav/pid-3327591-dt-content-rid-24486116_1/xid-24486116_1} (accessed 21st August).
 \vspace{0.2cm}

 \noindent [55] Parwal, R. (2023) \textit{The Risks of Performing No Testing or Minimal Testing} [online]. Available at \url{https://muuktest.com/blog/not-testing-software/} (accessed 21st August).
 \vspace{0.2cm}

 \noindent [56] Sketching Dev. (2023) \textit{Testing Pyramid} [online]. Available at \url{https://sketchingdev.co.uk/sketchnotes/testing-pyramid.html} (accessed 21st August).
 \vspace{0.2cm}

 \noindent [57] Pittet, S. (2023) \textit{The different types of software testing} [online]. Available at \url{https://www.atlassian.com/continuous-delivery/software-testing/types-of-software-testing} (accessed 21st August).
 \vspace{0.2cm}

 \noindent [58] Microsoft. (2023) \textit{Mocking in Unit Tests} [online]. Available at \url{https://microsoft.github.io/code-with-engineering-playbook/automated-testing/unit-testing/mocking/} (accessed 21st August).
 \vspace{0.2cm}

 \noindent [59] Google, Inc. (2023) \textit{Puppeteer} [online]. Available at \url{https://pptr.dev/} (accessed 21st August).
 \vspace{0.2cm}

 \noindent [60] Bierds, B. Gibson, J, et al. (2004). The Software Deployment Mystery - Solved: A Customer Guide. USA:IBM.
 \vspace{0.2cm}

 \noindent [61] Consensys. (2023) \textit{The crypto wallet for Defi, Web3 Dapps and NFTs | MetaMask} [online]. Available at \url{https://metamask.io/} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [62] Amazon Web Services. (2023) \textit{What Is Amazon EventBridge?} [online]. Available at \url{https://docs.aws.amazon.com/eventbridge/latest/userguide/eb-what-is.html} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [63] Amazon Web Services. (2023) \textit{What is AWS Lambda?} [online]. Available at \url{https://docs.aws.amazon.com/lambda/latest/dg/welcome.html} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [64] Stripe Inc. (2023) \textit{Stripe | Payment Processing Platform for the Internet} [online]. Available at \url{https://stripe.com/gb} (accessed 14th August).
 \vspace{0.2cm}

 \noindent [65] Frankenfield, J. (2022) \textit{Gas (Ethereum): How Gas Fees Work on the Ethereum Blockchain} [online]. Available at \url{https://www.investopedia.com/terms/g/gas-ethereum.asp} (accessed 21st August).
 \vspace{0.2cm}

\newpage
